Template for indicator documentation

### 2023-09-20 NDVI_wetland.Rmd
Change paths for bookdown

```{r, echo = F}
# downloading the unprocessed NDVI data from a data-cache et the NINA server
df.s <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/ndvi.Sentinel.raw.RDS")
df.m <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/ndvi.Modis.raw.RDS")
df.l <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/ndvi.Landsat.raw.RDS")
```

@@

```{r, echo = T, eval = F}
# Import Sentinel NDVI Data
df.s <- list.files("P:/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/NDVI_data_Sentinel/", pattern = "*.csv", full.names = TRUE) %>%
  map_df(~ fread(.))
```

@@

```{r, echo = T, eval = F}
# Import MODIS NDVI Data
# MODIS NDVI is scaled by 0.0001. Mean must be divided by 10000.
df.m <- read.csv("P:\\41201785_okologisk_tilstand_2022_2023\\data\\NDVI_åpenlavland\\NDVI_data_MODIS\\modis_ndvi_ts_2000_2022.csv", )
df.m$mean <- df.m$mean / 10000
```

>>>>

```{r, echo = F}
# downloading the unprocessed NDVI data from a data-cache et the NINA server
df.s <- readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/ndvi.Sentinel.raw.RDS")
df.m <- readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/ndvi.Modis.raw.RDS")
df.l <- readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/ndvi.Landsat.raw.RDS")
```

@@

```{r, echo = T, eval = F}
# Import Sentinel NDVI Data
df.s <- list.files("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/NDVI_data_Sentinel/", pattern = "*.csv", full.names = TRUE) %>%
  map_df(~ fread(.))
```

@@

```{r, echo = T, eval = F}
# Import MODIS NDVI Data
# MODIS NDVI is scaled by 0.0001. Mean must be divided by 10000.
df.m <- read.csv("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/NDVI_åpenlavland/NDVI_data_MODIS/modis_ndvi_ts_2000_2022.csv")
df.m$mean <- df.m$mean / 10000
```
